Ontology Matching with word2vec

### 2016-04-10 Paper/Draft.tex
Added current state & Current alignment strategies

 The group that requires high recall use hand-crafted knowledge bases, created by experts, containing only facts that are accurate, verified and relevant. This method of creating a knowledge base does not scale very well and usually consists of fewer than ten thousand facts. Because of this, the knowledge bases are restricted to small domains, including parts of medicine and cultural heritage. %TODO CITE en vind meer

 The group that requires a high recall, i.e. requires a huge amount of data, automated methods are required. These methods work fast, parsing thousands of websites a minute, but are inclined to make mistakes. Often, these methods use crowd-sourcing to improve accuracy, using experts or the general public to suggest or check facts. %TODO CITE

 Beside these knowledge bases, many other pieces of the Semantic Web are already in use. For example, the W3C %TODO OWL/RDF stats,

 Large ontologies already exist, with the largest, DBPedia, boasting almost two billion triples and the three hundred combined Large Open Data databases contain over thirty billion. %http://semantic-web-journal.net/system/files/swj499.pdf and http://lod-cloud.net/state/

 Leading scientists suggest that more research should be focused on

 %https://www.researchgate.net/profile/Hai_Dong/publication/260329617_Semantic_Web_Service_matchmakers_State_of_the_art_and_challenges/links/0a85e531190b602215000000.pdf

 Applications include
 %TODO vind meer en https://googleblog.blogspot.nl/2012/05/introducing-knowledge-graph-things-not.html

 Overall it is clear that % Samenvatten/enumerate, gevolg voor deze thesis (dus ik moet... mijn bijdrage is belangrijk...)
 \subsubsection{Technologies}
 \subsection{Ontologies}
 Earlier, ontologies were referred to as 'a set of rules that determine what relations are allowed and required.' Now, the term will be defined more extensively, the standard format will be described and the uses of ontologies will be discussed.

@@

 Popular terminological strategies are WordNet comparison and edit distance. The former uses the popular WordNet hierarchy as a distance measure between to concepts, e.g. the number of edges between the concepts and their least general common superconcept. % http://disi.unitn.it/~p2p/RelatedWork/Matching/Lin_WordNet_OM.pdf
 Edit distance is a purely string-based similarity measure. The similarity is a (weighted) count of edits required to transform one word into another, where common edits are insertion, deletion and replacement. Similar methods include substring matching and n-gram matching, which compare parts of the strings to find similarities. %http://disi.unitn.it/~p2p/RelatedWork/Matching/6614ijdms01.pdf
 \subsection{Problems in ontology alignment}
 \subsection{Other related research}
 \subsubsection{Word sense representation}
 Skip-gram models have been widely used to represent words as vectors. This is useful as it is easy to calculate the distance between two vectors, which is a useful property for ontology matching. This vector distance has been shown to be related to the semantic similarity between words. This semantic similarity is very useful for ontology alignment, as parts of one ontology have to be aligned with parts of another ontology depending on their semantic relation.

>>>>

 The group that requires high recall use hand-crafted knowledge bases, created by experts, containing only facts that are accurate, verified and relevant. This method of creating a knowledge base does not scale very well and usually consists of fewer than ten thousand facts. Because of this, the knowledge bases are restricted to small domains, including some parts of medicine and cultural heritage. \cite{byrne, le2002}

 The group that requires a high recall, i.e. requires a huge amount of data, automated methods are required. These methods work fast, parsing thousands of websites a minute, but are inclined to make mistakes. Often, these methods use crowd-sourcing to improve accuracy, using experts or the general public to suggest or check facts. \cite{zhou2007}

 Beside these knowledge bases, many other pieces of the Semantic Web are already in use. For example, the W3C \cite{rdf, owl}
 %TODO: stats?

 Large ontologies already exist, with the largest, DBPedia, boasting almost two billion triples and the three hundred combined Large Open Data databases contain over thirty billion. \cite{dbpedia, lod} The LOD is simply one huge alignment of hundreds of knowledge bases... %Doorschrijven

% Leading scientists suggest that more research should be focused on creating

 Applications include improved web searching, question answering, product comparison, context merging, data integration, decision support, translation, all the way up to the intelligent softbot mentioned earlier.

 % Elke behandelen

 Overall it is clear that % Samenvatten/enumerate, gevolg voor deze thesis (dus ik moet... mijn bijdrage is belangrijk...)
 \subsubsection{Technologies}

 \subsection{Ontologies}
 Earlier, ontologies were referred to as 'a set of rules that determine what relations are allowed and required.' Now, the term will be defined more extensively, the standard format will be described and the uses of ontologies will be discussed.

@@

 Popular terminological strategies are WordNet comparison and edit distance. The former uses the popular WordNet hierarchy as a distance measure between to concepts, e.g. the number of edges between the concepts and their least general common superconcept. \cite{lin2008}
 Edit distance is a purely string-based similarity measure. The similarity is a (weighted) count of edits required to transform one word into another, where common edits are insertion, deletion and replacement. Similar methods include substring matching and n-gram matching, which compare parts of the strings to find similarities.\cite{singh2014, levenshtein}
 \subsection{Problems in ontology alignment}
 \subsection{Other related research}
 \subsubsection{Word sense representation}
 Skip-gram models have been widely used to represent words as vectors. This is useful as it is easy to calculate the distance between two vectors, which is a useful property for ontology matching. This vector distance has been shown to be related to the semantic similarity between words. This semantic similarity is very useful for ontology alignment, as parts of one ontology have to be aligned with parts of another ontology depending on their semantic relation.
